PRIMUS: Galaxy Environment on the Quiescent Fraction Evolution at $z < 0.8$

### 2014-09-10 qfenv_paper/qf_environment.tex
Additional changes to Comparison to Literature sec

In addition, the $f_{\mathrm{Q}}(\mathcal{M}_{\mathrm{fid}})$ evolution illustrates that the quiescent fraction at low redshift increases over cosmic time: $f_{\mathrm{Q}}(\mathcal{M}_{\mathrm{fid}}, z \sim 0.1) - f_{\mathrm{Q}}(\mathcal{M}_{\mathrm{fid}}, z \sim 0.7) \sim 0.1$. This significant quiescent fraction evolution suggests that internal mechanisms independent of environment are responsible for a significant amount of star-formation quenching. The $f_{\mathrm{Q}}(\mathcal{M}_{\mathrm{fid}})$ evolution in high density environment ($f_{\mathrm{Q}}(\mathcal{M}_{\mathrm{fid}}, z \sim 0.1) - f_{\mathrm{Q}}(\mathcal{M}_{\mathrm{fid}}, z \sim 0.7) \sim 0.12$) shows little additional evolution.

@@

@@

As we did for our $f_{\rm{Q}}$ analysis above, we extend our $f_{\rm{Q}}$ comparison to focus on the evolution of the quiescent fraction at $\mathcal{M}_{\rm{fid}} = 10^{10.5} \mathcal{M}_{\odot}$. In Figure \ref{fig:qffit_comp}, we plot  best-fit parameterization of $f_{\rm{red}}$ for high and low density environment from zCOSMOS, \cite{Iovino:2010aa} (square) and \cite{Kovac:2014aa} (triangle), and SDSS, \cite{Baldry:2006aa} (diamond). From \cite{Iovino:2010aa} we calculate $f_{\rm{red}} = 1-f_{\rm{blue}}$ using the best-fit $f_{\rm{blue}}$ from the mass bin $\mathcal{M} = 10^{10.3} - 10^{10.8} \mathcal{M}_{\odot}$. From \cite{Kovac:2014aa} we plot an estimated $f_{\rm{Q}}$ by applying the difference between SFR based and color based galaxy classifications to the best-fit $f_{\rm{red}}$ at $\mathcal{M} = 10^{10.5} \mathcal{M}_{\odot}$ for low ($\delta = 0.0$) and high density environment ($\delta = 1.5$). Similarly, from \cite{Baldry:2006aa} we plot $f_{\rm{Q}}$ derived from the best-fit $f_{\rm{red}}$ at $\mathcal{M} = 10^{10.5} \mathcal{M}_{\odot}$ for low ($\delta = 0.0$) and high density environment ($\delta = 1.0$). We also plot $f_{\rm{Q}}(\mathcal{M} \sim 10^{10.5} \mathcal{M}_{\odot})$ from \cite{geha12a}.

@@

Both Figure \ref{fig:qffit} and Figure \ref{fig:qffit_comp} illustrate that throughout the entire redshift range, high density environment has a significantly greater $f_{\rm{Q}}(\mathcal{M}_{\rm{fid}})$ than the lower density environment. This is in strong agreement with the zCOSMOS results from \cite{Cucciati:2010aa} and \cite{Kovac:2014aa} and suggests that galaxy populations in higher density environments at $z < 1.0$ have higher quenched fractions. As galaxy color serves as a proxy for SFR, our results support the existence of the color-density relation (\citealt{Cucciati:2010aa, Cooper:2010aa}) and debunk the suggestions that the color-density relation is a merely a reflection of the mass-density or morphology-density relation (\citealt{Scodeggio:2009aa, Tasca:2009aa}).

The zCOSMOS results also find that $f_{\rm{red}}$ in high density environments are greater overall than in low density environments. The same trend is observed in the PRIMUS results and will be discussed in detail later in Section \ref{sec:env_qf_evol}. Another significant trend observed in the zCOSMOS results is the significant mass dependence of the $f_{\rm{red}}$ and $f_{\rm{blue}}$ evolution. \cite{Iovino:2010aa} by examining $f_{\rm{blue}}(z)$ in different mass bins for group and isolated galaxies find significantly larger $f_{\rm{blue}}$ evolution at lower masses. In fact, \cite{Iovino:2010aa} finds no evolution in $f_{\rm{blue}}$ for $\mathcal{M} > 10^{10.9} \mathcal{M}_{\odot}$ for both group and isolated galaxies over the redshift range $0.4 < z < 0.9$. On the other hand, in the lowest mass bin ($10^{10.0} \mathcal{M}_{\odot} < \mathcal{M} < 10^{10.5} \mathcal{M}_{\odot}$) \cite{Iovino:2010aa} finds $f_{\rm{blue}}(z \sim 0.4) - f_{\rm{blue}}(z \sim 0.2) \sim 0.2$ for isolated galaxies and  $f_{\rm{blue}}(z \sim 0.4) - f_{\rm{blue}}(z \sim 0.2) \sim 0.1$ for group galaxies. In contrast, in each of the panels of Figure \ref{fig:qf}, we qualitatively find little mass dependence on the $f_{\rm{Q}}$ evolution for either low or high density environments. However, due to the distinct stellar mass completeness limits imposed at each redshift bin of our sample, subtle effects such as the mass dependence of the $f_{\rm{Q}}$ evolution are difficult to discern.

The similarity of the evolutionary trends at $\mathcal{M}_{\rm{fid}} = 10^{10.5} \: \mathcal{M}_{\odot}$ and $10^{11} \: \mathcal{M}_{\odot}$ conflicts with \cite{Iovino:2010aa} who find contrasting $f_{\rm{Q}}$ evolutions at $\mathcal{M} \sim 10^{11.0} \mathcal{M}_{\odot}$ and $\mathcal{M} \sim 10^{10.5} \mathcal{M}_{\odot}$,  for both group and isolated galaxies. In fact at their highest mass bin ($10^{10.9} - 10^{11.4} \mathcal{M}_{\odot}$), \cite{Iovino:2010aa} find no evolution for both environments: $f_{\rm{blue}}$ remains constant at $\sim 0.1$ within $z = 0.3 - 0.8$ for both group and isolated galaxy populations. Meanwhile in their mass bin most comparable to our $\mathcal{M}_{\rm{fid}} = 10^{10.5} \mathcal{M}_{\odot}$, they present an evolution of $\Delta f_{\rm{red}} \sim 0.1$ over $z = 0.5$ to $0.25$ for group galaxies and $\Delta f_{\rm{red}} \sim 0.3$ over $z = 0.55$ to $0.3$. Furthermore, while we find that the $f_{\rm{Q}}(z)_{\rm{high}} - f_{\rm{Q}}(z)_{\rm{low}}$ remains relatively constant at $\sim 0.1$ over the redshift range for both fiducial masses, \cite{Iovino:2010aa} finds $f_{\rm{blue}}(z)_{ \rm{isolated}} - f_{\rm{blue}}(z)_{\rm{group}}$ is much more significant at $\mathcal{M} \sim 10^{10.5} \mathcal{M}_{\odot}$ than at $\mathcal{M} \sim 10^{11} \mathcal{M}_{\odot}$, where they find no difference.

zCOSMOS results find a clear mass dependence in the $f_{\rm{blue}}$ evolution; however, the consistency in evolutionary trends when the fiducial mass is changed reveal that our $f_{\rm{Q}}$ evolution exhibits little mass dependence. Although our sample from SDSS and PRIMUS provides significantly larger statistics, due to the limited mass ranges probed in our mass-complete sample (e.g. $\mathcal{M} > 10^{10.5} \mathcal{M}_{\odot}$ for our $z \sim 0.7$ bin) it is difficult to dismiss the mass dependence observed in the zCOSMOS results.

Another trend we observe in both Figure \ref{fig:qffit} Figure \ref{fig:qffit_comp}, is that for both environments $f_{\rm{Q}}(\mathcal{M}_{\rm{fid}})$ increases as redshift decreases. This highlights the general increase of $f_{\rm{Q}}(\mathcal{M})$ as redshift decreases noted earlier. More importantly, by fitting our $f_{\rm{Q}}$ evolution and obtaining the value at the fiducial mass, we are able to quantify the total evolution of $f_{\rm{Q}}$ for both low and high density environments through $f_{\rm{Q}}(\mathcal{M}_{\rm{fid}}, z \sim 0.1) - f_{\rm{Q}}(\mathcal{M}_{\rm{fid}}, z \sim 0.7)$ for both environments. In Figure \ref{fig:qffit}, we find that $f_{\rm{Q}}$ evolves by a similar amount for both environments.

Considering that fixed aperture definition of environment is susceptible to contamination due to PRIMUS redshift errors, in Figure \ref{fig:qffit_comp}, we consider more stringent classification of high density environments extending the cut-off to $n_{\rm{env}} > 6, 9$. A more stringent classification significantly increases the $f_{\rm{Q}}(\mathcal{M}_{\rm{fid}})$ overall. The decrease in sample size that accompanies a purer high environment sample also increase the uncertainties. More importantly, a purer high environment classification reveals a more significant environment dependence of the $f_{\rm{Q}}$ evolution. With a purer the high environment classification, we find a steeper slope in the $f_{\rm{Q}}$ and a greater total $f_{\rm{Q}}$ evolution. From $ z \sim 0.7$, for the low density environment ($n_{\rm{env}} < 0.5$) $f_{\rm{Q}}$ increases by roughly $0.1$. At the highest environments, $f_{\rm{Q}}$ increases by roughly $0.25$. Therefore, the total evolution of $f_{\rm{Q}}(\mathcal{M}_{\rm{fid}})$ from $z \sim 0.7$ to $\sim 0.1$ show moderate environment dependence.

>>>>

In addition, the $f_{\mathrm{Q}}(\mathcal{M}_{\mathrm{fid}})$ evolution illustrates that the quiescent fraction in low density environment increases over cosmic time: $f_{\mathrm{Q}}(\mathcal{M}_{\mathrm{fid}}, z \sim 0.1) - f_{\mathrm{Q}}(\mathcal{M}_{\mathrm{fid}}, z \sim 0.7) \sim 0.1$. This significant quiescent fraction evolution for low density environment suggests that internal mechanisms, independent of environment, are responsible for a significant amount of star-formation quenching. Meanwhile, the $f_{\mathrm{Q}}(\mathcal{M}_{\mathrm{fid}})$ evolution in high density environment ($f_{\mathrm{Q}}(\mathcal{M}_{\mathrm{fid}}, z \sim 0.1) - f_{\mathrm{Q}}(\mathcal{M}_{\mathrm{fid}}, z \sim 0.7) \sim 0.12$) shows little additional evolution.

@@

In Figure \ref{fig:qffit_comp}, we plot  best-fit parameterization of $f_{\rm{red}}$ for high and low density environment from zCOSMOS, \cite{Iovino:2010aa} (square) and \cite{Kovac:2014aa} (triangle), and SDSS, \cite{Baldry:2006aa} (diamond) and \cite{geha12a} (cross). From \cite{Iovino:2010aa} we calculate $f_{\rm{red}} = 1-f_{\rm{blue}}$ using the best-fit $f_{\rm{blue}}$ from the mass bin $\mathcal{M} = 10^{10.3} - 10^{10.8} \mathcal{M}_{\odot}$. From \cite{Kovac:2014aa} we plot an estimated $f_{\rm{Q}}$ by applying the residual between SFR based and color based galaxy classifications to the best-fit $f_{\rm{red}}$ at $\mathcal{M} = 10^{10.5} \mathcal{M}_{\odot}$ for low ($\delta = 0.0$) and high density environment ($\delta = 1.5$). Similarly, from \cite{Baldry:2006aa} we plot $f_{\rm{Q}}$ derived from the best-fit $f_{\rm{red}}$ at $\mathcal{M} = 10^{10.5} \mathcal{M}_{\odot}$ for low ($\delta = 0.0$) and high density environment ($\delta = 1.0$). For \cite{geha12a}, we plot $f_{\rm{Q}}$ in their mass bin closest to $10^{10.5} \mathcal{M}_{\odot}$, $\mathcal{M} \sim 10^{10.55} \mathcal{M}_{\odot}$.
%Add sentence about how the varying environment classification helps with the comparison.

@@

In Figure \ref{fig:qf}, observing the $f_{\rm{Q}}$ evolution with respect mass reveal, qualitatively, little mass dependence in the evolution. Moreover, in Figure \ref{fig:qffit}, we illustrated that adjusting the fiducial mass only shifted the overall $f_{\rm{Q}}(\mathcal{M}_{\rm{fid}})$, but did change the $f_{\rm{Q}}$ evolutionary trend. The consistency in the $f_{\rm{Q}}$ evolutionary trends when the fiducial mass is changed suggest that $f_{\rm{Q}}$ evolution exhibit little mass dependence. In contrast to the weak mass dependence we observe in our results, \cite{Iovino:2010aa} find significantly different $f_{\rm{Q}}$ evolutions at $\mathcal{M} \sim 10^{11} \mathcal{M}_{\odot}$ and $\mathcal{M} \sim 10^{10.5} \mathcal{M}_{\odot}$, for both group and isolated galaxies. In fact at their highest mass bin ($10^{10.9} - 10^{11.4} \mathcal{M}_{\odot}$, \cite{Iovino:2010aa} find no evolution for both environments: constant $f_{\mathrm{blue}} \sim 0.1$ over $z = 0.3 - 0.8$ for both group and isolated galaxy populations.

Meanwhile in their mass bin most comparable to $\mathcal{M}_{\rm{fid}} \sim 10^10.5 \mathcal{M}_{\odot}$ ($10^{10.3} \mathcal{M}_{\odot} - 10^{10.8} \mathcal{M}_{\odot}$), \cite{Iovino:2010aa} finds that $f_{\rm{blue}}$ evolves by $\sim 0.1$ from $z = 0.5$ to $0.25$ for group galaxies and by $\sim 0.3$ from $z=0.55$ to $0.3$ for isolated galaxies as presented in Figure \ref{fig:qffit_comp}. Altogether, with mass bins beyond the fiducial masses we explore, \cite{Iovino:2010aa} find a strong mass dependence with $f_{\rm{Q}}$ evolving significantly more in lower mass bins. While our sample from PRIMUS provides larger statistics than zCOSMOS, the mass-completeness limits we impose on our sample limits the mass range we probe (e.g. $\mathcal{M} > 10^{10.5} \mathcal{M}_{\odot}$ for our $z \sim 0.7$ bin). Consequently our results cannot dismiss mass dependence in the $f_{\rm{Q}}$ evolution at lower masses.

In Figure \ref{fig:qffit} and Figure \ref{fig:qffit_comp} we quantified that throughout our redshift range, high density environment has a significantly greater $f_{\rm{Q}}(\mathcal{M}_{\rm{fid}})$ than the low density environment. Our findings are in agreement with the zCOSMOS results from \cite{Cucciati:2010aa} and \cite{Kovac:2014aa}. As illustrated in Figure \ref{fig:qffit_comp}, both \cite{Cucciati:2010aa} and \cite{Kovac:2014aa} find $f_{\rm{Q}}$ in high density environment significantly greater than $f_{\rm{Q}}$ at low density environment. Moreover, since galaxy color serves as a proxy for SFR, our results support the existence of the color-density relation (\citealt{Cucciati:2010aa, Cooper:2010aa}) and debunks the suggestion that the color-density relation is merely a reflection of the mass-density as \cite{Scodeggio:2009aa} suggests for $0.2 < z< 1.4$ in the Vimos VLT Deep Survey.
% Purposely not mentioning the lack of morphology-density relation for M>10^10.5Msun galaxies as argued in Tasca et al. 2009 in order to not bring up morphology.

In Section \ref{sec:qffit}, we pointed out that $f_{\rm{Q}}$ in low density environment evolved over cosmic time. From this trend we deduce that internal, environment independent, quenching mechanisms contribute to star-formation quenching in galaxy evolution. \cite{Iovino:2010aa} from zCOSMOS, plotted in Figure \ref{fig:qffit_comp}, also find that $f_{\rm{Q}}$ in low density environment increases over decrease in redshift. On the other hand \cite{Kovac:2014aa}, also from zCOSMOS, presents that $f_{\rm{Q}}$ in low density environment decreases over cosmic time. This disagreement persists even when we account for the galaxy classification discrepancies in Figure \ref{fig:qffit_comp}.

Furthermore, in Section \ref{sec:qffit}, by comparing the $f_{\rm{Q}}$ evolution between the lowest density environment and the highest density environment, we found moderate evidence for the existence of environment dependent quenching mechanisms.

@@
